\section*{Preface}
\thispagestyle{empty}

This laboratory notebook is the result of months of hard work and dedication. Putting it together, session by session has helped me to internalize and really learn the concepts that we have explored in class.\medskip

I know that the document itself is extremely long, but there is no need to read it all, just use the Table of Contents to locate the laboratory sessions, which are normally at the end of every section. Its length is due to the fact that this notebook was not conceived as a mere summary of the laboratory sessions, but as a course guide with walked-through examples to help me grasp the basics of Digital Electronics.\medskip

I sincerely hope that you enjoy it as much as I have ejoyed piercing it together. If you have any questions, feel free to send me an e-mail, and I will gladly answer them.\medskip

Before diving into the document there are some remarks that must be made to better understand the contents of the notebook:


\begin{itemize}
    \item \textbf{ALL} of the images, tables, and figures are vectorial, so feel free to zoom in if something is not big enough. It turns out that finding good-quality vectorial images on the Inernet is not as easy as it may seem, so most of them have been created by me. Please excuse any mistakes that may have arised in the process of creating them. 
    
    \item There are \textbf{MULTIPLE} animations throughout the document, therefore it is highly recommended to use Adobe Acrobat Reader, or any other PDF reader (Not a browser), so as to be able to properly view the document.
    
    \item The document is plagued with crossed references and hyperlinks to other sections, tables and images. This was done in favour of avoiding having to explain the same concept multiple times. External references were also used to elaborate this notebook. The full reference list, in IEEE standard, can be found at the end of the document.
    
    \item Most of files can be downloaded \textbf{\href{https://drive.google.com/drive/folders/1nyozHdgMbIUZzLSXmLZj1Xq8IMVYWvJI?usp=sharing}{by clicking on this hyperlink}}.
    
    \item Since I did not want the document to have a huge size, NO PNGs or other non-vectorial images have been added. Please refer to the Google Drive link above to view them, if you wish so.
    
\end{itemize}\medskip

Let me finish by saying that I have really enjoyed this subject. It was something oblivious to me until the beginning of the course and I find myself really liking it now, thanks in large part to both of you. I hope that our paths meet again in the future. Thanks for everything,\bigskip

Alex

\bigskip




\clearpage
